---
title: "Sci-Expo Survey 2025-2026"
editor: source
date: ""
author: ""
toc: true
toc-depth: 5
# toc-expand: true
number-sections: true
highlight-style: pygments
toc-location: left
reference-location: margin
citation-location: margin
format:
  html: 
    code-fold: true
    html-math-method: katex
---


```{r preamble}
#| echo: false
#| include: false

library(ggplot2)
library(ggsignif)
library(dplyr)
library(readxl)
library(here)
library(Hmisc)

data_dir <- file.path(here(), "Data")
table_dir <- file.path(here(), "Tables")
```

```{r functions}
#| echo: false
#| include: false

responses_str_to_nbr <- function(response_str) {
  likert_1_str <- c("Strongly disagree", 
                    "Extremely unlikely", 
                    "Not at all represented")
  likert_2_str <- c("Somewhat disagree", 
                    "Somewhat unlikely", 
                    "A little bit represented")
  likert_3_str <- c("Neither agree nor disagree", 
                    "Neither likely nor unlikely", 
                    "Somewhat represented")
  likert_4_str <- c("Somewhat agree", 
                    "Somewhat likely", 
                    "Mostly represented")
  likert_5_str <- c("Strongly agree", 
                    "Extremely likely", 
                    "Completely represented")
  
  response_nbr <- case_when(
    response_str %in% likert_1_str ~ 1,
    response_str %in% likert_2_str ~ 2,
    response_str %in% likert_3_str ~ 3,
    response_str %in% likert_4_str ~ 4,
    response_str %in% likert_5_str ~ 5,
  )
}
```

# Demographics

```{r merge-datasets}
#| echo: false
#| include: false

# Load Data
pre_raw.df <- read_excel(file.path(data_dir, "SciExpo - Pre-Test ANON - 2025 (Responses).xlsx"), skip = 1) 
post_raw.df <- read_excel(file.path(data_dir, "SciExpo - Post-Test ANON - 2025 (Responses).xlsx"), skip = 1)

# Rename the columns appropriately
pre_raw.df <- pre_raw.df %>%
  select(!...2) %>% 
  relocate(survey_id) 
names(pre_raw.df)[2:20] <- paste0(names(pre_raw.df)[2:20], "_pre")

post_raw.df <- post_raw.df %>%
  select(!...2) %>% 
  relocate(survey_id) 
names(post_raw.df)[2:20] <- paste0(names(post_raw.df)[2:20], "_post")

# Check number of rows and unique entries
n_row_pre <- nrow(pre_raw.df)
n_unique_ids_pre <- length(unique(pre_raw.df$survey_id))

n_row_post <- nrow(post_raw.df)
n_unique_ids_post <- length(unique(post_raw.df$survey_id))

sprintf("nbr of rows pre: %i", n_row_pre)
sprintf("nbr of unique IDs pre: %i", n_unique_ids_pre)
sprintf("nbr of rows post: %i", n_row_post)
sprintf("nbr of unique IDs post: %i", n_unique_ids_post)

count_rows_pre.df <- pre_raw.df %>% 
  count(survey_id) %>% 
  arrange(desc(n))
duplicate_row_id <- count_rows_pre.df %>% 
  filter(n == 2) %>% 
  .$survey_id

sprintf("survey id of duplicate row: %i", duplicate_row_id)

pre_raw_duplicate.df <- pre_raw.df %>% 
  filter(survey_id == duplicate_row_id)
print(pre_raw_duplicate.df)

sprintf("We only keep the first entry...")
pre_clean.df <- pre_raw.df %>% 
  filter(as.character(timestamp_pre) != "2025-10-09 10:56:59.474")

# Merge the pre and post datasets
combined_wide.df <- merge(pre_clean.df, post_raw.df, all = T)

## SSI 
ssi_long.df <- 
  tidyr::pivot_longer(
    combined_wide.df %>% select(survey_id, contains("ssi")), 
    cols = contains("ssi"),
    values_to = "response",
    names_to = c("questionnaire", "item_nbr", "item_id", "prepost"),
    names_pattern = "(.*)_(.*)_(.*)_(.*)"
    ) %>% 
  mutate(subscale = case_when(grepl("^p", item_id) ~ "Peformance", 
                              grepl("^i", item_id) ~ "Interest",
                              grepl("^c", item_id) ~ "Competence",
                              grepl("^r", item_id) ~ "Recognition"),
         subscale_item_nbr = as.character(gsub("^[a-z]", "",item_id)))

## Representation in Science 
representation.df <- 
  tidyr::pivot_longer(
    combined_wide.df %>% 
      select(survey_id, matches("likely|represented_in")), 
    cols = matches("likely|represented_in"),
    values_to = "response",
    names_to = c("questionnaire", "prepost"),
    names_pattern = "(.*)_([^_]+)"
    ) 
## Feedback
feedback.df <- 
  tidyr::pivot_longer(
    combined_wide.df %>% 
      select(survey_id, matches("feelings|valuable|to_improve|other_comments")), 
    cols = matches("feelings|valuable|to_improve|other_comments"),
    values_to = "response",
    names_to = "questionnaire"
    ) %>% 
  mutate(prepost = "post")
## Time stamps
timestamps.df <- 
  tidyr::pivot_longer(
    combined_wide.df %>% 
      select(survey_id, timestamp_pre, timestamp_post), 
    cols = matches("timestamp"),
    values_to = "timestamp",
    names_to = c("prepost"),
    names_pattern = "timestamp_(.*)",
    values_drop_na = T
    ) 
## Participant data
demographics_data.df <- combined_wide.df %>% 
  select(survey_id, under_represented, attend_sciexpo_this_year, 
         attend_sciexpo_last_year, current_grade, ap_science_enrolled) %>% 
  mutate(under_represented = ifelse(under_represented == "Yes", 
                                    "HURM", "Non-\nHURM")) %>% 
  mutate(under_represented = factor(under_represented, 
                                    levels = c("Non-\nHURM", "HURM")))

## Merge datasets
combined_long.df <- 
  bind_rows(ssi_long.df, representation.df, feedback.df) %>% 
  merge(., timestamps.df) %>% 
  merge(., demographics_data.df) %>% 
  mutate(prepost = factor(prepost, levels = c("pre", "post")), 
         item_nbr = as.numeric(item_nbr),
         subscale = ifelse(is.na(subscale), questionnaire, subscale)) %>% 
  arrange(survey_id, prepost, questionnaire, item_nbr) %>% 
  mutate(score = responses_str_to_nbr(response))
  
write.csv(combined_long.df, file = file.path(table_dir, "all_participants_long.csv"))
saveRDS(combined_long.df, file = file.path(table_dir, "all_participants_long.rds"))



```

```{r ids-which-sessions}
#| echo: false
#| include: false

# Find the IDs that are in both sessions
which_sessions.df <- combined_long.df %>% 
  filter(!is.na(score)) %>%
  select(survey_id, prepost, attend_sciexpo_this_year, attend_sciexpo_last_year, 
         under_represented) %>% 
  unique(.) %>% 
  group_by(survey_id, attend_sciexpo_this_year, attend_sciexpo_last_year,
           under_represented) %>% 
  dplyr::summarize(session_completed = paste(prepost, collapse = " & ")) %>% 
  ungroup()

which_sessions_count.df <- which_sessions.df %>% 
  count(session_completed)

which_sessions_count_by_attendance.df <- which_sessions.df %>% 
  count(session_completed, attend_sciexpo_this_year, attend_sciexpo_last_year,
        under_represented) %>% 
  mutate(attend_sciexpo_this_year = ifelse(attend_sciexpo_this_year == "Yes", 
                                           "Attended This Year", "Did NOT Attend This Year"), 
         attend_sciexpo_last_year = ifelse(attend_sciexpo_last_year == "Yes", 
                                           "Attended Last Year", "Did NOT Attend Last Year"),
         session_completed = ifelse(session_completed == "pre", "Pre Only", session_completed),
         session_completed = ifelse(session_completed == "post", "Post Only", session_completed),
         session_completed = ifelse(session_completed == "pre & post", "Pre & Post", session_completed),
         session_completed = factor(session_completed, 
                                    levels = c("Pre & Post", "Pre Only", "Post Only"))) %>% 
  relocate(attend_sciexpo_this_year, session_completed, attend_sciexpo_last_year, 
           under_represented) %>% 
  arrange(attend_sciexpo_this_year, session_completed, desc(attend_sciexpo_last_year)) %>% 
  mutate(included_in_baseline = ifelse(session_completed %in% c("Pre & Post", "Pre Only"),
                                       "In Baseline", ""),
         included_in_prepost = ifelse(session_completed == "Pre & Post" & 
                                        attend_sciexpo_this_year == "Attended This Year",
                                       "In Prepost", ""), 
         under_represented = gsub("\n", "", under_represented, fixed = T))
which_sessions_count_by_attendance.df

ids_in_both_sessions.df <- which_sessions.df %>% 
  filter(session_completed %in% c('pre', 'post')) %>% 
  .$survey_id
```

```{r under-represented-count}
#| echo: false
#| include: false

under_represented_count.df <- combined_long.df %>% 
  select(survey_id, under_represented) %>% 
  unique() %>% 
  count(under_represented)
n_nonhurm <- under_represented_count.df %>% filter(under_represented == "Non-\nHURM") %>% .$n
n_hurm <- under_represented_count.df %>% filter(under_represented == "HURM") %>% .$n
n_hurm_na <- under_represented_count.df %>% filter(is.na(under_represented)) %>% .$n

```

```{r keep-only-full-dataset}
#| echo: false
#| include: false

combined_long.df <- merge(combined_long.df, which_sessions.df)

combined_long_only_full_participants.df <- combined_long.df %>% 
  filter(!(session_completed %in% c('pre', 'post')))

attend_last_year_count.df <- combined_long_only_full_participants.df %>% 
  filter(attend_sciexpo_this_year == "Yes") %>% 
  select(survey_id, attend_sciexpo_last_year, under_represented) %>%
  unique(.) %>%
  count(attend_sciexpo_last_year, under_represented)
attend_last_year_count.df

write.csv(combined_long_only_full_participants.df, file = file.path(table_dir, "participants_who_answered_both_surveys_long.csv"))
saveRDS(combined_long_only_full_participants.df, file = file.path(table_dir, "participants_who_answered_both_surveys_long.rds"))


combined_wide_only_full_participants.df <-
  combined_long_only_full_participants.df %>% 
  group_by(survey_id, under_represented, subscale, attend_sciexpo_this_year, 
           attend_sciexpo_last_year, prepost, session_completed) %>% 
  summarise(score = mean(score)) %>% 
  tidyr::pivot_wider(names_from = c(subscale, prepost), 
                     names_sep = "_", 
                     values_from = score)

write.csv(combined_wide_only_full_participants.df, file = file.path(table_dir, "participants_who_answered_both_surveys_wide.csv"))
saveRDS(combined_wide_only_full_participants.df, file = file.path(table_dir, "participants_who_answered_both_surveys_wide.rds"))

```

In total, we collected responses from `r n_nonhurm` students, with `r n_hurm` from historically under-represented minorities (HURM) and `r n_nonhurm` not from historically under-represented minorities (Non-HURM). Note that we do not have this information for `r n_hurm_na` students because they only completed the post-test survey, and we only asked this information in the pre-test survey. 

The number of participants who completed each survey is as follows: 
```{r which-sessions-display}
#| echo: false

knitr::kable(which_sessions_count.df)
```

Detailed table of the number of participants who completed each survey, attended which sciexpo, and depending on their minority status: 
```{r which-sessions-detailed-display}
#| echo: false

knitr::kable(which_sessions_count_by_attendance.df)
# print(as.data.frame(which_sessions_count_by_attendance.df))
```

# Descriptives

```{r descriptive-functions}
#| echo: false
#| include: false

compute_dvs <- function(df, var) {
  output.df <- df %>%
    dplyr::reframe(mean = mean({{ var }}),
                   median = median({{ var }}), 
                   sd = sd({{ var }}), 
                   ci95_low = smean.cl.boot({{ var }})[2],
                   ci95_high = smean.cl.boot({{ var }})[3], 
                   n = n()) %>% 
    mutate(subscale_str_for_plot = case_when(
      subscale == "Competence" ~ "SSI\nCompetence", 
      subscale == "Interest" ~ "SSI\nInterest", 
      subscale == "Recognition" ~ "SSI\nRecognition", 
      subscale == "Peformance" ~ "SSI\nPeformance", 
      subscale == "likely_become_scientist" ~ "Likely\nScientist", 
      subscale == "represented_in_science" ~ "Science\nRepresentation", 
    ))
  return(output.df)
}

make_subscale_names_for_plot <- function(df) {
  output.df <- df %>% 
    mutate(subscale_str_for_plot = case_when(
      subscale == "Competence" ~ "SSI\nCompetence", 
      subscale == "Interest" ~ "SSI\nInterest", 
      subscale == "Recognition" ~ "SSI\nRecognition", 
      subscale == "Peformance" ~ "SSI\nPeformance", 
      subscale == "likely_become_scientist" ~ "Likely\nScientist", 
      subscale == "represented_in_science" ~ "Science\nRepresentation", 
    ))
  return(output.df)
}

```

```{r descriptive-plot-function}
#| echo: false
#| include: false

make_descriptive_plot <- function(data, title_str = NULL, version = "prepost") {
  prepost_descriptives.plot <- ggplot(data = data) +
    geom_col(aes(x = under_represented, y = mean, fill = under_represented, 
                 alpha = prepost), 
             position = position_dodge(width = 0.8), width = 0.7) + 
    geom_errorbar(aes(x = under_represented, ymin = ci95_low, ymax = ci95_high, group = prepost),
                  position = position_dodge(width = 0.8), width = 0.3) +
    geom_point(aes(x = under_represented, y = mean, group = prepost),
                  position = position_dodge(width = 0.8), size = 1.5) + 
    facet_grid(. ~ subscale_str_for_plot) + 
    ylab("Score") + 
    ylim(0,5) +
    theme_bw() + 
    theme(axis.title.x = element_blank(), legend.position = "none") + 
    scale_fill_manual(values = c("#648FFF", "#DC267F")) + 
    scale_alpha_manual(values = c(0.7, 1))
  
  if(!is.null(title_str)) {
    prepost_descriptives.plot <- prepost_descriptives.plot + 
      ggtitle(title_str)
  }
    
  return(prepost_descriptives.plot)
}

make_descriptive_violin_plot <- function(data, data_raw, title_str = NULL, version = "prepost", 
                                         color_scale = c("#648FFF", "#DC267F")) {

  prepost_descriptives.plot <- ggplot(data = data) +
    geom_violin(data = data_raw, 
                aes(x = under_represented, y = score_aggregate, color = under_represented, alpha = prepost), 
             position = position_dodge(width = 0.8)) + 
    geom_jitter(data = data_raw, 
                aes(x = under_represented, y = score_aggregate, color = under_represented, alpha = prepost), 
                position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.8), size = 0.5) + 
    geom_errorbar(aes(x = under_represented, ymin = ci95_low, ymax = ci95_high, group = prepost),
                  position = position_dodge(width = 0.8), width = 0.3) +
    geom_point(aes(x = under_represented, y = mean, group = prepost),
                  position = position_dodge(width = 0.8), size = 3, shape = 4) + 
    facet_grid(. ~ subscale_str_for_plot) + 
    ylab("Score") + 
    ylim(0,5) +
    theme_bw() + 
    theme(axis.title.x = element_blank(), legend.position = "none") + 
    scale_color_manual(values = color_scale) + 
    scale_alpha_manual(values = c(0.7, 1))
  
  if(!is.null(title_str)) {
    prepost_descriptives.plot <- prepost_descriptives.plot + 
      ggtitle(title_str)
  }
    
  return(prepost_descriptives.plot)
}

```

## Baseline descriptives

```{r baseline-descriptives}
#| echo: false
#| include: false

baseline_long_by_participant.df <- combined_long.df %>% 
  filter(prepost == "pre", 
         !is.na(score)) %>%
  group_by(survey_id, questionnaire, subscale, under_represented, prepost,
           attend_sciexpo_this_year, attend_sciexpo_last_year) %>% 
  dplyr::summarise(score_aggregate = mean(score))
```

### Students who did not attend last year

```{r baseline-plot-not-last-year}
#| echo: false
#| include: false

baseline_long_aggregated_not_last_year.df <- 
  baseline_long_by_participant.df %>% 
  group_by(questionnaire, subscale, under_represented, prepost,
           attend_sciexpo_last_year) %>% 
  compute_dvs(score_aggregate)

baseline_long_aggregated_not_last_year.df <- 
  baseline_long_aggregated_not_last_year.df %>% 
  filter(attend_sciexpo_last_year == "No")

sample_sizes_all.df <- baseline_long_aggregated_not_last_year.df %>% 
  select(under_represented, n) %>% 
  unique()
n_nonhurm <- sample_sizes_all.df %>% filter(under_represented == "Non-\nHURM") %>% .$n
n_hurm <- sample_sizes_all.df %>% filter(under_represented == "HURM") %>% .$n

baseline_descriptives_not_last_year.plot <- 
  make_descriptive_plot(data = baseline_long_aggregated_not_last_year.df, 
                        title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", 
                                            n_nonhurm, n_hurm), 
                        version = "baseline")

baseline_long_by_participant_not_last_year.df <- 
  baseline_long_by_participant.df %>% 
  filter(attend_sciexpo_last_year == "No") %>% 
  make_subscale_names_for_plot()

baseline_descriptives_not_last_year_violin.plot <- 
  make_descriptive_violin_plot(
    data = baseline_long_aggregated_not_last_year.df, 
    data_raw = baseline_long_by_participant_not_last_year.df,
    title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", n_nonhurm, n_hurm), 
    version = "baseline")


```

```{r baseline-plot-not-last-year-display}
#| echo: false
#| fig-cap: "Baseline values for students who did not attend last year's expo - Bar plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

baseline_descriptives_not_last_year.plot
```

```{r baseline-violin-plot-not-last-year-display}
#| echo: false
#| fig-cap: "Baseline values for students who did not attend last year's expo - Violin plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

baseline_descriptives_not_last_year_violin.plot
```

### Students regardless of last year's attendance

#### Aggregated

```{r baseline-plot-all-students-aggregated}
#| echo: false
#| include: false

baseline_long_aggregated_all_students_aggregated.df <- 
  baseline_long_by_participant.df %>% 
  group_by(questionnaire, subscale, under_represented, prepost) %>% 
  compute_dvs(score_aggregate)

sample_sizes_all.df <- baseline_long_aggregated_all_students_aggregated.df %>% 
  select(under_represented, n) %>% 
  unique()
n_nonhurm <- sample_sizes_all.df %>% filter(under_represented == "Non-\nHURM") %>% .$n
n_hurm <- sample_sizes_all.df %>% filter(under_represented == "HURM") %>% .$n

baseline_descriptives_all_students_aggregated.plot <- 
  make_descriptive_plot(data = baseline_long_aggregated_all_students_aggregated.df, 
                        title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", 
                                            n_nonhurm, n_hurm), 
                        version = "baseline")


baseline_long_by_participant_all.df <- 
  baseline_long_by_participant.df %>% 
  make_subscale_names_for_plot()

baseline_descriptives_all_students_aggregated_violin.plot <- 
  make_descriptive_violin_plot(
    data = baseline_long_aggregated_all_students_aggregated.df, 
    data_raw = baseline_long_by_participant_all.df,
    title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", n_nonhurm, n_hurm), 
    version = "baseline")

```

```{r baseline-plot-all-students-aggregated-display}
#| echo: false
#| fig-cap: "Baseline values for all students regardless of expo attendance - Bar plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

baseline_descriptives_all_students_aggregated.plot
```

```{r baseline-violin-plot-all-students-aggregated-display}
#| echo: false
#| fig-cap: "Baseline values for all students regardless of expo attendance - Violin plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

baseline_descriptives_all_students_aggregated_violin.plot
```

#### Split by last year's attendance 

```{r baseline-plot-any_attendance-split}
#| echo: false
#| include: false

baseline_long_aggregated_all_students_split.df <- 
  baseline_long_by_participant.df %>% 
  group_by(questionnaire, subscale, under_represented, prepost, 
           attend_sciexpo_last_year) %>% 
  compute_dvs(score_aggregate)

sample_sizes_all.df <- baseline_long_aggregated_all_students_split.df %>% 
  select(under_represented, attend_sciexpo_last_year, n) %>% 
  unique()
n_nonhurm_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "Non-\nHURM" & attend_sciexpo_last_year == "Yes") %>% 
  .$n
n_nonhurm_not_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "Non-\nHURM" & attend_sciexpo_last_year == "No") %>% 
  .$n
n_hurm_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "HURM" & attend_sciexpo_last_year == "Yes") %>% 
  .$n
n_hurm_not_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "HURM" & attend_sciexpo_last_year == "No") %>% 
  .$n

baseline_long_aggregated_all_students_split.df <-  
  baseline_long_aggregated_all_students_split.df %>% 
  mutate(attend_sciexpo_last_year = 
           ifelse(attend_sciexpo_last_year == "Yes", 
                  "Attended\nlast year", "Did NOT attend\nlast year")) %>% 
  mutate(attend_sciexpo_last_year = 
           factor(attend_sciexpo_last_year, 
                  levels = c("Did NOT attend\nlast year", "Attended\nlast year")))

baseline_descriptives_all_students_split.plot <- 
  make_descriptive_plot(baseline_long_aggregated_all_students_split.df, 
                        title_str = sprintf("N(Non-HURM) = %i (Did NOT attend) / %i (Attended);\nN(HURM) = %i (Did NOT attend) / %i (Attended)",
                                          n_nonhurm_not_last_year, n_nonhurm_last_year, 
                                          n_hurm_not_last_year, n_hurm_last_year)) +
  facet_grid(attend_sciexpo_last_year ~ subscale_str_for_plot)

baseline_long_by_participant_all.df <- 
  baseline_long_by_participant.df %>% 
  make_subscale_names_for_plot() %>% 
  mutate(attend_sciexpo_last_year = 
           ifelse(attend_sciexpo_last_year == "Yes", 
                  "Attended\nlast year", "Did NOT attend\nlast year")) %>% 
  mutate(attend_sciexpo_last_year = 
           factor(attend_sciexpo_last_year, 
                  levels = c("Did NOT attend\nlast year", "Attended\nlast year")))

baseline_descriptives_all_students_split_violin.plot <- 
  make_descriptive_violin_plot(
    data = baseline_long_aggregated_all_students_split.df, 
    data_raw = baseline_long_by_participant_all.df,
    title_str = sprintf("N(Non-HURM) = %i (Did NOT attend) / %i (Attended);\nN(HURM) = %i (Did NOT attend) / %i (Attended)", 
                                          n_nonhurm_not_last_year, n_nonhurm_last_year, 
                                          n_hurm_not_last_year, n_hurm_last_year)) +
  facet_grid(attend_sciexpo_last_year ~ subscale_str_for_plot)

```

```{r baseline-plot-any_attendance-split-display}
#| echo: false
#| fig-cap: "Baseline values for all students split by last year's expo attendance - Bar plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

baseline_descriptives_all_students_split.plot
```

```{r baseline-violin-plot-any_attendance-split-display}
#| echo: false
#| fig-cap: "Baseline values for all students split by last year's expo attendance - Violin plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

baseline_descriptives_all_students_split_violin.plot
```

## Prepost descriptives

```{r prepost-descriptives}
#| echo: false
#| include: false

prepost_long_by_participant.df <- combined_long.df %>% 
  filter(session_completed == "pre & post", 
         !is.na(score)) %>%
  group_by(survey_id, questionnaire, subscale, under_represented, prepost, 
           attend_sciexpo_last_year, attend_sciexpo_this_year) %>% 
  dplyr::summarise(score_aggregate = mean(score))
```

### Students who only attended this year

```{r prepost-plot-only-this-year}
#| echo: false
#| include: false

prepost_long_aggregated_correct_attendance.df <- 
  prepost_long_by_participant.df %>% 
  group_by(questionnaire, subscale, under_represented, prepost, 
           attend_sciexpo_last_year, attend_sciexpo_this_year) %>% 
  compute_dvs(score_aggregate)

prepost_long_aggregated_correct_attendance.df <- 
  prepost_long_aggregated_correct_attendance.df %>% 
  filter(attend_sciexpo_last_year == "No" & attend_sciexpo_this_year == "Yes")

sample_sizes_all.df <- prepost_long_aggregated_correct_attendance.df %>% 
  select(under_represented, n) %>% 
  unique()
n_nonhurm <- sample_sizes_all.df %>% filter(under_represented == "Non-\nHURM") %>% .$n
n_hurm <- sample_sizes_all.df %>% filter(under_represented == "HURM") %>% .$n


prepost_descriptives_only_this_year.plot <- 
    make_descriptive_plot(prepost_long_aggregated_correct_attendance.df, 
                    title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", 
                                        n_nonhurm, n_hurm))

prepost_long_by_participant_correct_attendance.df <- 
  prepost_long_by_participant.df %>% 
  make_subscale_names_for_plot() %>% 
  filter(attend_sciexpo_last_year == "No" & attend_sciexpo_this_year == "Yes")

prepost_descriptives_only_this_year_violin.plot <- 
  make_descriptive_violin_plot(
    data = prepost_long_aggregated_correct_attendance.df, 
    data_raw = prepost_long_by_participant_correct_attendance.df,
    title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", 
                                        n_nonhurm, n_hurm))

```

```{r prepost-plot-only-this-year-display}
#| echo: false
#| fig-cap: "Prepost values for students who attended this year's exop and did not attend last year's expo - Bar plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

prepost_descriptives_only_this_year.plot
```

```{r prepost-violin-plot-only-this-year-display}
#| echo: false
#| fig-cap: "Prepost values for students who attended this year's exop and did not attend last year's expo - Violin plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

prepost_descriptives_only_this_year_violin.plot
```

### Students who attended this year, regardless of last year's attendance

#### Aggregated

```{r prepost-plot-any_attendance-aggregated}
#| echo: false
#| include: false

prepost_long_aggregated_any_attendance.df <- 
  prepost_long_by_participant.df %>% 
  group_by(questionnaire, subscale, under_represented, prepost, 
           attend_sciexpo_this_year) %>% 
  compute_dvs(score_aggregate)

prepost_long_aggregated_any_attendance.df <- 
  prepost_long_aggregated_any_attendance.df %>% 
  filter(attend_sciexpo_this_year == "Yes")

sample_sizes_all.df <- prepost_long_aggregated_any_attendance.df %>% 
  select(under_represented, n) %>% 
  unique()
n_nonhurm <- sample_sizes_all.df %>% filter(under_represented == "Non-\nHURM") %>% .$n %>% sum()
n_hurm <- sample_sizes_all.df %>% filter(under_represented == "HURM") %>% .$n %>% sum()

prepost_descriptives_any_attendance.plot <- 
    make_descriptive_plot(prepost_long_aggregated_any_attendance.df, 
                    title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", 
                                        n_nonhurm, n_hurm))


prepost_long_by_participant_all.df <- 
  prepost_long_by_participant.df %>% 
  make_subscale_names_for_plot()

prepost_descriptives_any_attendance_violin.plot <- 
  make_descriptive_violin_plot(
    data = prepost_long_aggregated_any_attendance.df, 
    data_raw = prepost_long_by_participant_all.df,
    title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", 
                                        n_nonhurm, n_hurm))

```

```{r prepost-plot-any_attendance-aggregated-display}
#| echo: false
#| fig-cap: "Prepost values for all students regardless of expo attendance - Bar plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

prepost_descriptives_any_attendance.plot

```

```{r prepost-violin-plot-any_attendance-aggregated-display}
#| echo: false
#| fig-cap: "Prepost values for all students regardless of expo attendance - Violin plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

prepost_descriptives_any_attendance_violin.plot
```

#### Split by last year's attendance 

```{r prepost-plot-any_attendance-split}
#| echo: false
#| include: false

prepost_long_split_any_attendance.df <- 
  prepost_long_by_participant.df %>% 
  group_by(questionnaire, subscale, under_represented, prepost, 
           attend_sciexpo_last_year, attend_sciexpo_this_year) %>% 
  compute_dvs(score_aggregate)

prepost_long_split_any_attendance.df <- 
  prepost_long_split_any_attendance.df %>% 
  filter(attend_sciexpo_this_year == "Yes")

sample_sizes_all.df <- prepost_long_split_any_attendance.df %>% 
  select(under_represented, attend_sciexpo_last_year, n) %>% 
  unique()
n_nonhurm_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "Non-\nHURM" & attend_sciexpo_last_year == "Yes") %>% 
  .$n
n_nonhurm_not_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "Non-\nHURM" & attend_sciexpo_last_year == "No") %>% 
  .$n
n_hurm_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "HURM" & attend_sciexpo_last_year == "Yes") %>% 
  .$n
n_hurm_not_last_year <- 
  sample_sizes_all.df %>% 
  filter(under_represented == "HURM" & attend_sciexpo_last_year == "No") %>% 
  .$n

prepost_long_split_any_attendance.df <-  
  prepost_long_split_any_attendance.df %>% 
  mutate(attend_sciexpo_last_year = 
           ifelse(attend_sciexpo_last_year == "Yes", 
                  "Attended\nlast year", "Did NOT attend\nlast year")) %>% 
  mutate(attend_sciexpo_last_year = 
           factor(attend_sciexpo_last_year, 
                  levels = c("Did NOT attend\nlast year", "Attended\nlast year")))

prepost_descriptives_any_attendance_split.plot <- 
  make_descriptive_plot(prepost_long_split_any_attendance.df, 
                      title_str = sprintf("N(Non-HURM) = %i (Did NOT attend) / %i (Attended);\nN(HURM) = %i (Did NOT attend) / %i (Attended)",
                                          n_nonhurm_not_last_year, n_nonhurm_last_year, 
                                          n_hurm_not_last_year, n_hurm_last_year)) +
  facet_grid(attend_sciexpo_last_year ~ subscale_str_for_plot)



prepost_long_by_participant_all.df <- 
  prepost_long_by_participant.df %>% 
  make_subscale_names_for_plot() %>% 
  mutate(attend_sciexpo_last_year = 
           ifelse(attend_sciexpo_last_year == "Yes", 
                  "Attended\nlast year", "Did NOT attend\nlast year")) %>% 
  mutate(attend_sciexpo_last_year = 
           factor(attend_sciexpo_last_year, 
                  levels = c("Did NOT attend\nlast year", "Attended\nlast year")))

prepost_descriptives_any_attendance_split_violin.plot <- 
  make_descriptive_violin_plot(
    data = prepost_long_split_any_attendance.df, 
    data_raw = prepost_long_by_participant_all.df,
    title_str = sprintf("N(Non-HURM) = %i (Did NOT attend) / %i (Attended);\nN(HURM) = %i (Did NOT attend) / %i (Attended)", 
                                          n_nonhurm_not_last_year, n_nonhurm_last_year, 
                                          n_hurm_not_last_year, n_hurm_last_year)) +
  facet_grid(attend_sciexpo_last_year ~ subscale_str_for_plot)

```

```{r prepost-plot-any_attendance-split-display}
#| echo: false
#| fig-cap: "Prepost values for all students split by last year's expo attendance - Bar plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

prepost_descriptives_any_attendance_split.plot
```

```{r prepost-violin-plot-any_attendance-split-display}
#| echo: false
#| fig-cap: "Prepost values for all students split by last year's expo attendance - Violin plot. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

prepost_descriptives_any_attendance_split_violin.plot
```

# Analyses 

## Science Representation

First, let's focus on *Science Representation*, the only measure that seems to show any difference between pre-test and post-test. We performed a Repeated-Measure ANOVA with Time (pre/post) as within-subject factor and Minority Status (HURM/Non-HURM) as between-subject factor on all subjects who attended the expo in 2025 (this year) regardless of attendance in 2024 (last year). We found a main effect of time (F(1, 55)=14.49, p<0.001, eta^2^=0.034) and Minority Status (F(1, 55)=14.49, p<0.001, eta^2^=0.193), while the interaction was not significant (F(1, 55)=2.82, p=0.01, eta^2^=0.007).

Post-hoc tests revealed that *Science Representation* was increased for the whole sample from pre-test to post-test (t(55) = 3.806, p < 0.001), with a medium effect size (Cohen's d = 0.417, CI95 = [0.185; 0.649]). *Science Representation* was also higher for the Non-HURM sutdents compared to the HURM students (t(55) = 4.081, p < 0.001), with a very large effect size (Cohen's d = 0.999, CI95 = [0.473; 1.526]),  P-values are adjusted with Holm's correction.


```{r science-rpz-only-violin-plot-with-signif}
#| include: false
#| echo: false

prepost_analyses_any_attendance_violin_rpz_in_science.plot <- 
  make_descriptive_violin_plot(
    data = prepost_long_aggregated_any_attendance.df %>% 
      filter(subscale == "represented_in_science") %>% 
      mutate(under_represented = paste(under_represented, prepost, sep = "-"), 
             under_represented = factor(under_represented, 
                                        levels = c("Non-\nHURM-pre", "Non-\nHURM-post", "HURM-pre", "HURM-post"))), 
    data_raw = prepost_long_by_participant_all.df  %>% 
      filter(subscale == "represented_in_science") %>% 
      mutate(under_represented = paste(under_represented, prepost, sep = "-"), 
             under_represented = factor(under_represented, 
                                        levels = c("Non-\nHURM-pre", "Non-\nHURM-post", "HURM-pre", "HURM-post"))), 
    title_str = sprintf("N(Non-HURM) = %i; N(HURM) = %i", 
                                        n_nonhurm, n_hurm), 
    color_scale = c("#648FFF", "#648FDF", "#DC267F", "#DC265F")) + 
  geom_signif(
    data =prepost_long_by_participant_all.df  %>% 
      filter(subscale == "represented_in_science") %>% 
      mutate(under_represented = paste(under_represented, prepost, sep = "-"), 
             under_represented = factor(under_represented, 
                                        levels = c("Non-\nHURM-pre", "Non-\nHURM-post", "HURM-pre", "HURM-post"))), 
    mapping = aes(x = under_represented, y = score_aggregate),
    annotations = c("n.s", "p = 0.010", "p < 0.001", "p = 0.003"), 
    comparisons = list(c("HURM-pre", "HURM-post"), 
                       c("HURM-pre", "Non-\nHURM-pre"),
                       c("HURM-post", "Non-\nHURM-post"),
                       c("Non-\nHURM-pre", "Non-\nHURM-post")),
    y_position = c(5.1, 5.6, 6.1, 5.1),
    map_signif_level = T      # Manually set the vertical position (optional)
  ) +
  ylim(0, 6.5)

```

```{r science-rpz-only-violin-plot-with-signif-display}
#| echo: false
#| fig-cap: "Prepost values for all students regardless last year's expo attendance for Science Representation. The difference between HURM and Non-HURM student is significant, as well as the overall pre-post effect. P-values come from post-hoc t-tests. HURM -> Historically Under-Represented Minority. Error bars are 95CI"
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true

prepost_analyses_any_attendance_violin_rpz_in_science.plot

```


## Can we use the 8 students who did not attend this year’s expo as a ctrl grp?

Ideally, to ensure that any effect observed on our DVs (and specifically *Science Representation*) is not due to any factor that may have naturally occurred during the 4 weeks between the pre-test and post-test survey (other than the Science Expo), we would compare the pre-post change in *Science Representation* between students that attended the expo and matched students who did not attend the expo. While we did not include such a group in our original design, eight (8) students in our sample completed the pre-test and post-test surveys but did not attend the expo.

Note that out of these 8 students, 2 are Non-HURM and 6 are HURM students. Because of this very low sample in the sample of participants who did not attend the expo this year, we do not split this analysis between Non-HURM and HRUM students. While the interaction is not significant (due to the very small size of the group of students who did not attend last year's expo), numerically it seems that the group who did not attend this expo this year did not see any change in *Science Representation* compared to the group who did attend the expo this year. 

We note that almost all students who did not attend the expo this year reported below average values in *Science Representation*, and thus it is possible that the reason why we do not see any difference between pre-test and post-test for this group is that they might either be not interested in research in the first place, and so their feeling of *Science Representation* possibly cannot be changed anyway. 

```{r science-rpz-only-violin-plot-with-not-attended-group}
#| echo: false
#| include: false

combined_long_only_full_participants.df <- 
  readRDS(file = file.path(table_dir, "participants_who_answered_both_surveys_long.rds"))


combined_long_only_full_participants_science_rpz.df <- 
  combined_long_only_full_participants.df %>% 
  filter(questionnaire == "represented_in_science") %>% 
  rename(score_aggregate = score)

combined_long_only_full_participants_science_rpz_aggregated.df <- 
  combined_long_only_full_participants_science_rpz.df %>% 
  group_by(questionnaire, subscale, prepost,
           attend_sciexpo_this_year) %>% 
  compute_dvs(score_aggregate)


prepost_analyses_any_attendance_violin_rpz_in_science.plot <- 
  ggplot(data = combined_long_only_full_participants_science_rpz_aggregated.df) +
  geom_violin(data = combined_long_only_full_participants_science_rpz.df, 
              aes(x = attend_sciexpo_this_year, y = score_aggregate, color = prepost), 
           position = position_dodge(width = 0.8)) + 
  geom_jitter(data = combined_long_only_full_participants_science_rpz.df, 
              aes(x = attend_sciexpo_this_year, y = score_aggregate, color = prepost), 
              position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.8), size = 0.5) + 
  geom_errorbar(aes(x = attend_sciexpo_this_year, ymin = ci95_low, ymax = ci95_high, group = prepost),
                position = position_dodge(width = 0.8), width = 0.2) +
  geom_point(aes(x = attend_sciexpo_this_year, y = mean, group = prepost),
                position = position_dodge(width = 0.8), size = 3, shape = 4) + 
  geom_line(aes(x = attend_sciexpo_this_year, y = mean, group = attend_sciexpo_this_year), 
            position = position_dodge2(width = 0.8)) + 
  facet_grid(. ~ subscale_str_for_plot) + 
  ylab("Score") + 
  ylim(0,5) +
  theme_bw() + 
  theme(axis.title.x = element_blank(), legend.position = "none") + 
  scale_color_manual(values = c("pre" = "#999999", "post" = "#000000")) + 
  scale_x_discrete(labels = c("No" = "Did NOT Attend Expo\nThis Year (2025)", 
                              "Yes" = "Attended Expo\nThis Year (2025)"))
  
```


```{r science-rpz-only-violin-plot-with-not-attended-group-display}
#| echo: false
#| fig-cap: "Pre-test and post-test Science Representation of students who attended this year's expo compare to student who did not attend this year's expo (ad hoc control group), included all students regardless of last year's expo attendance or minority status. Error bars are 95CI."
#| cap-location: margin
#| out.width: "95%"
#| fig.align: "center"
#| cache: true


prepost_analyses_any_attendance_violin_rpz_in_science.plot


```


# Open-Feedback Analyses

```{r}
#| include: false
#| echo: false

combined_long.df <- readRDS(file = file.path(table_dir, "all_participants_long.rds")) 
combined_long_feedback.df <- combined_long.df %>% 
  filter(prepost == "post", 
         questionnaire %in% 
           c("feelings_change_after_sciexpo", 
             "sciexpo_most_valuable_aspects",
             "sciexpo_other_comments",
             "sciexpo_what_to_improve"), 
         attend_sciexpo_this_year == "Yes", 
         !is.na(response)) %>% 
  select(survey_id, prepost, questionnaire, response, subscale, under_represented, attend_sciexpo_this_year, attend_sciexpo_last_year) %>% 
  mutate(under_represented = gsub("\n", "", under_represented, fixed = T)) %>% 
  arrange(questionnaire, under_represented)

```

## Feelings Change After Expo

Question : *After attending the Science Expo, how has seeing yourself being represented, or not represented, in the scientific community influenced your perception or feelings about your own place in science?*

Mixed results, quick look at the table seems to show about half of the students had their feelings changes and the other half not really. Overall, I would say enough students report being motivated by this expo to pursue their careers that it seems worth it. 


```{r feelings-change-table-display}
#| echo: false

knitr::kable(combined_long_feedback.df %>% 
               filter(questionnaire == "feelings_change_after_sciexpo") %>% 
               select(response, under_represented))
```

## Most Valuable Aspects

Question : *What aspects of the Science Expo did you find most valuable? *

- Variety of booths, 
- Interactivity
- Candies

```{r most-valubale-aspects-table-display}
#| echo: false

knitr::kable(combined_long_feedback.df %>% 
               filter(questionnaire == "sciexpo_most_valuable_aspects") %>% 
               select(response, under_represented))
```

## What to Improve

Question : *What aspects of the Expo would you improve and how?*

Main themes : 
- More hands-on tables
- More tables overall
- More candy
- A bunch of people said they liked it, and one of them even said they'd want more throughout the year :D 
- One comment about pronouns

```{r what-to-improve-table-display}
#| echo: false

knitr::kable(combined_long_feedback.df %>% 
               filter(questionnaire == "sciexpo_what_to_improve") %>% 
               select(response, under_represented))
```

## Other Comments

Question : *Any other comments or reflections you want to share with the organizers?*

```{r other-comments-table-display}
#| echo: false

knitr::kable(combined_long_feedback.df %>% 
               filter(questionnaire == "sciexpo_other_comments") %>% 
               select(response, under_represented))
```
